\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-25 bare_conf.tex
small fixes.

\textcolor{red}{This paper is structured as follows. Section~\ref{sec:method}, describes the methodological foundations of this research. Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system. Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.}

@@

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way. \textcolor{red}{For instance, detected objects could be presented to the user in a configurable order, based on the importance of particular object classes to the user or other personalized criteria.} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

Similar functionality has been previously addressed by research communities \cite{Caraiman}-\cite{Zientara} and industry \cite{orcam}\cite{horus}. The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image and video processing tasks. While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband. The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make this limitation obsolete, especially in densely populated areas containing many hazards for the blind. Moreover, increasing computational power of smartphones may also allow to perform more advanced image and video processing locally. \textcolor{red}{Although not always technically feasible, local  processing is especially important in low connectivity areas to ensure at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.

>>>>

This paper is structured as follows. Section~\ref{sec:method} describes the methodological foundations of this research. Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system. Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.

@@

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarify how various types of guidance information should be represented to the user in the most convenient and efficient way. For instance, detected objects could be presented to the user in a configurable order, based on the importance of particular object classes to the user or other personalized criteria. USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

Similar functionality has been previously addressed by research communities \cite{Caraiman}-\cite{Zientara} and industry \cite{orcam}\cite{horus}. The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image and video processing tasks. While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband. The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make this limitation obsolete, especially in densely populated areas containing many hazards for the blind. Moreover, increasing computational power of smartphones may also allow to perform more advanced image and video processing locally. Although not always technically feasible, local  processing is especially important in low connectivity areas to ensure at least partial functionality of the system. Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
